IIIDYT at IEST 2018: Implicit Emotion Classification With Deep Contextualized Word Representations

### 2018-07-30 paper/paper.tex
Update Paper, bibliografy, rsync_ignore
Update bibliography, write some intro paragraphs

\documentclass[11pt,a4paper]{article}
\usepackage[hyperref]{emnlp2018}
% \usepackage[showframe=true]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{times}
\usepackage{latexsym}
\usepackage{lipsum}
\usepackage{url}
\usepackage{multirow}
\usepackage{changepage}
\usepackage{amssymb}
\usepackage{bm}
\usepackage{amsmath}
\usepackage[hang,flushmargin]{footmisc} % remove indentation from footnotes
% \hypersetup{draft}

@@

@@

\section{Introduction}
\begin{itemize}
    \item High level description of the task~\cite{klinger2018iest} and its \textit{raison d'être}
        (Francés para Edison)
    \item High level description of the model used and results obtained
\end{itemize}

\section{Related Work}
\begin{itemize}
    \item briefly describe previous Wassa papers~\cite{baziotis2018ntua,
        duppada2018seernet, abdou2018affecthor} (Should we do this despite not
        having based our work in any of them?)
    \item Talk about elmo~\cite{peters2018deep}
\end{itemize}

@@

@@

>>>>

\documentclass[11pt,a4paper]{article}
\usepackage[hyperref]{emnlp2018}
% \usepackage[showframe=true]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{times}
\usepackage{latexsym}
\usepackage{lipsum}
\usepackage{url}
\usepackage{multirow}
\usepackage{changepage}
\usepackage{amssymb}
\usepackage{bm}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[hang,flushmargin]{footmisc} % remove indentation from footnotes
% \hypersetup{draft}

@@

% Style for acronyms; avoids splitting them.
% See https://tex.stackexchange.com/questions/48435/how-do-i-prevent-tex-from-hyphenating-acronyms
\newcommand{\Acronym}[1]{\mbox{#1}}

@@

\section{Introduction}

% FIXME: EDIT THIS SECTION TO MAKE PARAGRAPHS MORE COHESIVE
Sentiment Analysis, also known as Opinion Mining, is a discipline whose
objective is to automatically identify sentiment in written text
\cite{balazs2016opinion}.

The \Acronym{WASSA} 2018 Implicit Emotion Shared Task
(\Acronym{IEST})~\cite{klinger2018iest}, consists in predicting the emotion of a
word that has been excluded from a tweet. Its aim is to find ways to
automatically learn the link between situations and the emotion they trigger.

This problem can be reduced to sentence classification, in which we
want to classify a sentence, or more specifically a tweet, into one of several
categories.

In this paper we present the system that obtained second place, proposed by the
team \Acronym{IIIDYT} at \Acronym{IEST}\@. Our system was composed by a single
pre-trained \Acronym{ELMo} layer for encoding words~\cite{peters2018deep}, a
Bidirectional Long-Short Memory Network
(\Acronym{BiLSTM})~\cite{graves2005framewise, graves2013speech}, for enriching
word representations with context, a max-pooling operation for creating sentence
representations from said word vectors, and finally a Dense Layer for projecting
the sentence representations into label space (See
Figure~\ref{fig:architecture}).

\section{Related Work}
\begin{itemize}
    \item briefly describe previous Semeval papers~\cite{baziotis2018ntua,
        duppada2018seernet, abdou2018affecthor} (Should we do this despite not
        having based our work in any of them?)
    \item mention previous Wassa papers
    \item talk about some sentence classification tasks? Works that fall into
        the broad category of mapping sentences to labels.
    \item Talk about elmo~\cite{peters2018deep}
\end{itemize}

@@

\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{images/best_ensembles.eps}
\caption{Best Macro F1 vs. Number of Ensembled Models}
\label{fig:}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{images/average_ensembles.eps}
\caption{Best Macro F1 vs. Number of Ensembled Models}
\label{fig:}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{images/iest_architecture.pdf}
    \caption{Proposed architecture}
    \label{fig:architecture}
\end{figure}

@@

\begin{table}[!h]
    \centering
    \footnotesize

    \begin{tabular}{lcc}

        \textbf{Variation} & \textbf{Accuracy (\%)} & $\bf{\Delta}$\textbf{\%} \\
        \hline
        \hline
        Submitted          & \textbf{69.23}         & -               \\
        \hline
        No emoji           & 68.36                  & - 0.87          \\
        \hline
        No ELMo            & 65.52                  & - 3.71          \\
        \hline
        Concat Pooling     & 68.47                  & - 0.76          \\
        \hline
        LSTM hidden=4096   & 69.10                  & - 0.13          \\
        LSTM hidden=1024   & 68.93                  & - 0.30          \\
        LSTM hidden=512    & 68.43                  & - 0.80          \\
        \hline
        POS emb dim=100    & 68.99                  & - 0.24          \\
        POS emb dim=75     & 68.61                  & - 0.62          \\
        POS emb dim=50     & 69.33                  & + 0.10          \\
        POS emb dim=25     & 69.21                  & - 0.02          \\

    \end{tabular}
    \caption{Ablation study results}

\end{table}
